Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-05-14 Phase_II/draft/II.tex
edits

The significance of the signal can be expressed in terms of the signal-to-noise ratio (SNR), which depends on many factors. However, most importantly, it does not depend on the optical bandwidth $\Delta {\mathrm {\nu}}$ of the radiation for a two-telescope correlation. The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided in several works \citep[e.g.,][subsection 4.1 of][]{10.1093/mnras/stab2391}.  The Signal-to-Noise is given by
\begin{equation}
	SNR = A \cdot \alpha \cdot q \cdot n \cdot F^{-1} \cdot \sigma \cdot \sqrt{\frac{T \Delta f}{2}} \cdot \abs{V_{12}}^{2}
	\label{eq:SNR}
\end{equation}
Here, $A$ is the total mirror area, $\alpha$ is the quantum efficiency of the PMTs, $q$ is the throughput of the remaining optics, and $n$ is the differential photon flux from the source. The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep[e.g.,][]{acciari2020optical}. The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
\begin{equation}
	S = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
\end{equation}
and
\begin{equation}
	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}.
\end{equation}
While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes is to increase the observation time $T$.

>>>>

The significance of the signal can be expressed in terms of the signal-to-noise ratio (SNR), which depends on many factors. However, most importantly, it does not depend on the optical bandwidth $\Delta {\mathrm {\nu}}$ of the radiation for a two-telescope correlation. The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided in several works \citep[e.g., subsection 4.1 of][]{10.1093/mnras/stab2391}.  The Signal-to-Noise is given by
\begin{equation}
	SNR = A \cdot \alpha \cdot q \cdot n \cdot F^{-1} \cdot \sigma \cdot \sqrt{\frac{T \Delta f}{2}} \cdot \abs{V_{12}}^{2}
	\label{eq:SNR}
\end{equation}
Here, $A$ is the total mirror area, $\alpha$ is the quantum efficiency of the PMTs, $q$ is the throughput of the remaining optics, and $n$ is the differential photon flux from the source. The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep[e.g.,][]{acciari2020optical}. The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
\begin{equation}
	S = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
\end{equation}
and
\begin{equation}
	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}.
\end{equation}
While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes is to increase the observation time $T$.
